---
title: "R Notebook"
output: html_notebook
---
# Initial Trends

```{r}
library(readr)
library(rlist)

library(extrafont) 
library(tidyverse)

# execute once to add fonts:
# font_import() 

loadfonts(device='win')
windowsFonts("Latex" = windowsFont("CMU Serif"))

salvage_list = list.load("../../Datasets/salvage_list.RData")
Sal_CTDC = read_csv("../../Datasets/SalvagedCTDC.csv")
CTDC = read_csv("../../Datasets/CTDC.csv")[-1]
CTDC <- CTDC %>% relocate(CountryOfExploitation, .after = citizenship)
```

```{r}
sal_counts = data.frame("Category" = c("Sexual Exploit","Labour Exploit",
                                       "Means of Control", "recruiter Relation"),
                        
                        "Salvaged Rows" = c(length(salvage_list$sexSalvaged),
                                            length(salvage_list$labourSalvaged),
                                      length(salvage_list$meanscontrolSalvaged),
                                      length(salvage_list$recruiterSalvaged))
)
sal_counts
```

```{r}
nul_vec = rep(0, nrow(CTDC))
sex_sal_ind = nul_vec
lab_sal_ind = nul_vec
moc_sal_ind = nul_vec
rec_sal_ind = nul_vec


for (i in 1:nrow(CTDC)){
  if (i %in% salvage_list$sexSalvaged){
    sex_sal_ind[i] = 1
  }
}

for (i in 1:nrow(CTDC)){
  if (i %in% salvage_list$labourSalvaged){
    lab_sal_ind[i] = 1
  }
}

for (i in 1:nrow(CTDC)){
  if (i %in% salvage_list$meanscontrolSalvaged){
    moc_sal_ind[i] = 1
  }
}

for (i in 1:nrow(CTDC)){
  if (i %in% salvage_list$recruiterSalvaged){
    rec_sal_ind[i] = 1
  }
}


salvaged_mask = data.frame("Sexual Exploit" = sex_sal_ind,
                           "Labour Exploit" = lab_sal_ind,
                           "Means of Control" = moc_sal_ind,
                           "Recruiter Relation" = rec_sal_ind)

salvaged_mask$citizenship = CTDC$citizenship
salvaged_mask$CountryOfExploitation = CTDC$CountryOfExploitation
```

Remove rows that are not salvaged

```{r}
del = c(0)

for (rowid in 1:nrow(salvaged_mask)){
  row = salvaged_mask[rowid,]
  if (sum(row[,1:4]) == 0){
    del = append(del,rowid)
  } 
}

salvaged_mask = salvaged_mask[-del,]
```



Intersection Plots

```{r}

salvaged_mask2 = salvaged_mask



salvaged_mask2[which(!(salvaged_mask2$CountryOfExploitation %in% c("PH","UA","MD","US",NA, "RU"))),]$CountryOfExploitation = "Other"

salvaged_mask2[which(!(salvaged_mask2$citizenship %in% c("PH","UA","MD","US",NA, "RU"))),]$citizenship = "Other"

salvaged_mask2[which(is.na(salvaged_mask2$citizenship)),]$citizenship = "Unknown"
salvaged_mask2[which(is.na(salvaged_mask2$CountryOfExploitation)),]$CountryOfExploitation = "Unknown"

salvaged_mask2
```



```{r}
library(ggplot2)
library(ComplexUpset)

# Save File
png(file="./Graphics/SalvageRowsUpset.png",width = 1200, height = 900, res = 200)

# Categories to plot
cats = colnames(salvaged_mask2)[1:4]

# Levels to Plot
lvls = c("Unknown","MD",'RU',"US",'PH','UA','Other')

#Color Pallate

pallate = c("MD"="#13294B", "US" = "#4B9CD3",
            "RU"="#4F758B", "PH" = "#00594C",
            "UA" = "#EF426F", "Other" = "#ac643c",
            "Unknown" = "#F4E8DD")

upset(salvaged_mask2, cats, name='Variable Categories', width_ratio=0.1,
      set_sizes=FALSE,
      base_annotations=list(
        'Salvaged Rows'=intersection_size(counts=FALSE) +
          theme(text = element_text(family = "Latex", size = 12))
    ),
      
      
      annotations = list(
        'Country of Exploitation'=(
             ggplot(mapping=aes(fill=factor(CountryOfExploitation,
                                            levels = lvls)))
            + geom_bar(stat='count', position='fill')
            + scale_y_continuous(labels=scales::percent_format())
            + theme(legend.position="none",
                    text = element_text(family = "Latex", size = 12)) 
            + ylab("Country of \n Exploitation")
            + scale_fill_manual(values=pallate)
            ),
        
        'Citizenship'=(
             ggplot(mapping=aes(fill=factor(citizenship,
                                            levels = lvls)))
            + geom_bar(stat='count', position='fill')
            + scale_y_continuous(labels=scales::percent_format())
            + theme(text = element_text(family = "Latex", size = 12)) 
            + ylab("Citizenship") 
            + scale_fill_manual(name = "Country",
                                values=pallate,
                                drop = FALSE))
        )
    ) + theme(text = element_text(family = "Latex", size = 12))

#ggsave(file='./Graphics/SalvageRowsUpset.png', width = 8, height = 5)
dev.off()
```

```{r}
Sal_CTDC_Fac = Sal_CTDC[-c(1,2)]

for (i in 1:ncol(Sal_CTDC_Fac)){
  Sal_CTDC_Fac[i] = as.factor(Sal_CTDC_Fac[[i]])
}

```

Factor Analysis


Treat DTM as numeric, drop year, datasource, majority variables
```{r}
ModelData1 = Sal_CTDC_Fac[-c(1,2,5:7)]

ModelData1$exploitationDTM = as.numeric(as.character(ModelData1$exploitationDTM))

ModelData1$citizenshipDTM = as.numeric(as.character(ModelData1$citizenshipDTM))

# Remove NA values from dtm

ModelData1 = ModelData1[which(ModelData1$exploitationDTM != -1),]
ModelData1 = ModelData1[which(ModelData1$citizenshipDTM != -1),]
```

```{r}
LMOD1 = lm(exploitationDTM ~ ., data = ModelData1[-53])
drop1(LMOD1, test = "F")[c(5,6)]
mean(abs(predict(LMOD1)-ModelData1$exploitationDTM))
```

# Repeat Analysis From Earlier With NEw Dataset

```{r}
library(ggplot2)
library(readr)

library(extrafont) 
library(tidyverse)

# execute once to add fonts:
# font_import() 

loadfonts(device='win')
windowsFonts("Latex" = windowsFont("CMU Serif"))

CTDC.2 = Sal_CTDC
```



Visuals for DTM Stage

```{r}
CTDC.2$citizenshipDTM = as.factor(CTDC.2$citizenshipDTM)
CTDC.2$exploitationDTM = as.factor(CTDC.2$exploitationDTM)
```


DTM Stages Data
```{r}
library(gridExtra)

# Citizenship DTM Barplot
cit_dtm_plot = ggplot(CTDC.2, aes(citizenshipDTM)) +
  geom_bar() + theme_grey(base_size = 16) +
  theme(axis.text = element_text(size = 9),
    text = element_text(family = "Latex", size = 15)) + 
   scale_fill_grey() +
  labs(x = "Citizenship DTM Stage", y = "Count")

# Exploit DTM Barplot
exp_dtm_plot = ggplot(CTDC.2
, aes(exploitationDTM)) +
  geom_bar() + theme_grey(base_size = 16) +
  theme(axis.text = element_text(size = 9),
    text = element_text(family = "Latex", size = 15),
    axis.ticks.y=element_blank(),
    axis.text.y=element_blank()) + 
   scale_fill_grey() +
  labs(x = "Exploitation DTM Stage", y = element_blank())

#merge both plots within one grid
g <- gridExtra::grid.arrange(cit_dtm_plot, exp_dtm_plot, ncol = 2)
ggsave(file='./Graphics/SalDTMStagesBarplot.jpg', g, width = 8, height = 4)#saves g
```

Country for Each Stage

```{r}
# Citizenship DTM Barplot
cit_country_plot = ggplot(CTDC.2[which(CTDC.2$citizenshipDTM!=-1),], aes(citizenshipDTM, fill = fct_rev(fct_infreq(citizenship)))) +
  geom_bar(position="dodge", width=0.9) + theme_grey(base_size = 16) +
  theme(axis.text = element_text(size = 9),
    text = element_text(family = "Latex", size = 15),
    legend.position = "none") + 
   scale_fill_manual(values=rep("#605c5c", 100)) +
  labs(x = "Citizenship DTM Stage", y = "Count of Each Country")


exp_country_plot = ggplot(CTDC.2[which(CTDC.2$exploitationDTM!=-1),],
  aes(exploitationDTM, fill = fct_rev(fct_infreq(CountryOfExploitation)))) +
  geom_bar(position="dodge", width=0.9) + theme_grey(base_size = 16) +
  theme(axis.text = element_text(size = 9),
    text = element_text(family = "Latex", size = 15),
    axis.ticks.y=element_blank(),
    axis.text.y=element_blank(),
    legend.position = "none") + 
   scale_fill_manual(values=rep("#605c5c", 100)) +
  labs(x = "Exploitation DTM Stage", y = element_blank())

#merge both plots within one grid
g <- gridExtra::grid.arrange(cit_country_plot, exp_country_plot, ncol = 2)
ggsave(file='./Graphics/SalCountryCountBarplot.png', g, width = 8, height = 4)
```

Find overpowering stage 5 country

```{r}
# Citizenship DTM Country
t = table(CTDC.2[CTDC.2$citizenshipDTM == 4,]$citizenship)
t[t == max(t)]

# Exploitation DTM Country
t = table(CTDC.2[CTDC.2$exploitationDTM == 4,]$CountryOfExploitation)
t[t == max(t)]
```

Comparing Russia to Other stage 5 exploitation Chi Square:

```{r}
stage5exp = CTDC.2[CTDC.2$exploitationDTM == 5,]
not_RU = which(stage5exp$CountryOfExploitation != 'RU')
stage5exp$CountryOfExploitation[not_RU] = 'N_RU'

c = chisq.test(stage5exp$CountryOfExploitation, stage5exp[[5]])
c
```


```{r, warning = F}
#Initialize Dataframe
chisq_dataframe = data.frame(VariableName = c(1),
                             ChiSquared = c(1),
                             PValue = c(1))


for (i in c(1:ncol(stage5exp))){
  #Remove columns for country names and citizenship dtm
  #----------------------
  ignored_columns = c('citizenship', "CountryOfExploitation",
                      'citizenshipDTM', 'exploitationDTM')
  
  # If columns has 1 unique value, then ignore
  
  if (length(unique(stage5exp[[i]]))==1){
    ignored_columns = append(ignored_columns, names(stage5exp)[i])
  }
  
  # If column isnt in ignored columns
  if (!(names(stage5exp)[i] %in% ignored_columns)){
    c = chisq.test(stage5exp$CountryOfExploitation, stage5exp[[i]])
    
    # Add Row To Table
    chisq_dataframe[nrow(chisq_dataframe) + 1,] = 
    c(names(stage5exp)[i],c$statistic, c$p.value)
  }
  


}
# Change Class and Remove Initial Row
chisq_dataframe$ChiSquared = as.numeric(chisq_dataframe$ChiSquared)
chisq_dataframe$PValue = as.numeric(chisq_dataframe$PValue)
chisq_dataframe = chisq_dataframe[-c(1),]

write.csv(chisq_dataframe, "./Graphics/ChiSquareDF1.csv")
```


Repeat For Citizenship

```{r}
stage5cit = CTDC.2[CTDC.2$citizenshipDTM == 5,]
not_UA = which(stage5exp$citizenship != 'UA')
stage5cit$citizenship[not_RU] = 'N_UA'

#Initialize Dataframe
chisq_dataframe = data.frame(VariableName = c(1),
                             ChiSquared = c(1),
                             PValue = c(1))


for (i in c(1:ncol(stage5cit))){
  #Remove columns for country names and citizenship dtm
  #----------------------
  ignored_columns = c('citizenship', "citizenship",
                      'citizenshipDTM', 'exploitationDTM')
  
  # If columns has 1 unique value, then ignore
  
  if (length(unique(stage5cit[[i]]))==1){
    ignored_columns = append(ignored_columns, names(stage5cit)[i])
  }
  
  # If column isnt in ignored columns
  if (!(names(stage5exp)[i] %in% ignored_columns)){
    c = chisq.test(stage5cit$citizenship, stage5cit[[i]])
    
    # Add Row To Table
    chisq_dataframe[nrow(chisq_dataframe) + 1,] = 
    c(names(stage5cit)[i],c$statistic, c$p.value)
  }
  


}
# Change Class and Remove Initial Row
chisq_dataframe$ChiSquared = as.numeric(chisq_dataframe$ChiSquared)
chisq_dataframe$PValue = as.numeric(chisq_dataframe$PValue)
chisq_dataframe = chisq_dataframe[-c(1),]
chisq_dataframe

write.csv(chisq_dataframe, "./Graphics/ChiSquareDF2.csv")
```



```{r}
ggplot(CTDC.2, aes(citizenshipDTM, fill = exploitationDTM)) +
  geom_bar() + theme_grey(base_size = 16) +
  theme(axis.text = element_text(size = 9),
    text = element_text(family = "Latex", size = 15)) + 
   scale_fill_grey() +
  labs(x = "Citizenship DTM Stage", y = "Count", fill = "Exploitation DTM")
  
ggsave(file='./Graphics/DTMStage1.png', width = 8, height = 4)
```

Count how many cases have same citizenship and exploitation country.
```{r}
nrow(CTDC.2[CTDC.2$citizenship == CTDC.2$CountryOfExploitation,])
nrow(CTDC.2)
nrow(CTDC.2[CTDC.2$citizenship == CTDC.2$CountryOfExploitation,])/nrow(CTDC.2)
```


Same Country
```{r}
diff_country = CTDC.2[!(CTDC.2$citizenship == CTDC.2$CountryOfExploitation),]

ggplot(diff_country, aes(citizenshipDTM, fill = exploitationDTM)) +
  geom_bar() + theme_grey(base_size = 16) +
  theme(axis.text = element_text(size = 9),
    text = element_text(family = "Latex", size = 15)) + 
   scale_fill_grey() +
  labs(x = "Citizenship DTM Stage", y = "Count", fill = "Exploitation DTM")
  
ggsave(file='./Graphics/Different_CountryDTM.png', width = 8, height = 4)
```

Correlation Plot

```{r}
#Select Numeric Only
cor_df = CTDC.2[sapply(CTDC.2, class) != 'character']
cor_df$citizenshipDTM = as.numeric(cor_df$citizenshipDTM)
cor_df$exploitationDTM = as.numeric(cor_df$exploitationDTM)

library("Hmisc") # Gives P-Values for correlation
res2 <- rcorr(as.matrix(cor_df))


corr = res2$r # Correlations
corr_p = res2$P # P-values
```

Correlation Plot
```{r}
library(ggcorrplot)
library(ggplot2)

ggcorrplot(corr, colors = c("#242424", "#E7E7E7", "#242424"),
           tl.cex = 11, tl.srt = 90, show.diag = F,
          p.mat = corr_p, legend.title = "Correlation",
          ggtheme = ggplot2::theme_classic) +
  
  theme(text = element_text(family = "Latex", size = 12),
        axis.text.x = element_text(vjust = 0.1, hjust = 1),
        panel.background = element_rect(fill = '#242424'))

ggsave(file='./Graphics/CorrPlot.png', width = 7, height = 7)
```

More Visualizations

```{r}

```





Binary Percentage Visualization

```{r}
# Create Binary Percentage Dataframe
bin_perc <- CTDC.2 %>% group_by(exploitationDTM) %>% 
  summarise(across(names(CTDC.2[5:23]),sum),
            .groups = 'drop') %>%
  as.data.frame()

bin_perc = (bin_perc/nrow(CTDC.2))[2:ncol(bin_perc)]
```


```{r}
# Gather Dataframe and Add DTM Stages

gath <- bin_perc %>%
  as_data_frame()%>%
  gather(key = "variable", value = "value")

gath$exploitationDTM = rep(c(2,3,4,5),times = nrow(gath)/4)
```

Create Facet Plot
```{r}
# Make Facet Plot
ggplot(gath, aes(x = exploitationDTM,
           y = value)) +
    facet_wrap(~ variable, ncol = 3) +
    geom_bar(stat = "identity",
           position = "dodge") + theme_grey(base_size = 16) +
  theme(axis.text = element_text(size = 9),
    text = element_text(family = "Latex", size = 15)) + 
   scale_fill_grey()+
  labs(y= "Proportion", x = "Exploitation Country DTM Stage",
       title =  "Proportion of Type & Stage Out Of All Cases")

ggsave(file='./Graphics/FacetPlot1.png', width = 8.5, height = 10)
```

