---
title: "Quasi Variable Analysis"
output: html_notebook
---

# Initializing Packages and Functions
```{r}
library(readr)
library(dplyr)
CTDC = read_csv("../../Datasets/CTDC.csv")[-1]
CTDC <- CTDC %>% relocate(CountryOfExploitation, .after = citizenship)
head(CTDC)
```

```{r}
library(ggplot2)

library(extrafont) 
library(tidyverse)

# execute once to add fonts:
# font_import() 

loadfonts(device='win')
windowsFonts("Latex" = windowsFont("CMU Serif"))
```

Remove Columns Function
```{r}
removed = c()

remove_columns <- function(remove){
  # Add Removed Columns to Removed List

  removed <<- append(unique(removed), remove)
  
  features = names(CTDC)

  # Update features to only include kept variables
  features = c(setdiff(features, remove))
  
  # Update CTDC to only have kept features
  CTDC <<- CTDC[features]
}
```

# Add DTM Stage to Data Set


Create dataframe with Alpha-2 codes,and DTM stage
```{r}
codes = read_csv("../../Datasets/CountryCodes.csv")
dtm = read_csv("../../Datasets/Countries_Data2.0.csv")[c(2,14)]

###### left join in R using merge() function 
df = merge(x=codes,y=dtm, by.x="Alpha-3 code", by.y = "Code", all.x=TRUE)
Code_DTM = df[c(3,6)]
```



Add column in CTDC with DTM stage for "countryOfExploitation"
```{r}

CTDC = merge(x=CTDC,y=Code_DTM, by.x="CountryOfExploitation", by.y = "Alpha-2 code", all.x=TRUE)

#rename DTM_Stage to exploitationDTM
names(CTDC)[ncol(CTDC)] = "exploitationDTM"
```

Add column in CTDC with DTM stage for "citizenship"
```{r}
CTDC = merge(x=CTDC,y=df, by.x="citizenship", by.y = "Alpha-2 code", all.x=TRUE)

#rename DTM_Stage to citizenshipDTM
names(CTDC)[ncol(CTDC)] = "citizenshipDTM"
```

Remove Unnecessary Joined Data


```{r}
remove = c("Alpha-3 code",
           "Numeric code","English short name lower case"
           ,"ISO 3166-2")

remove_columns(remove)
```

# Remove Concatonated Variables



```{r}
remove = c('meansOfControlConcatenated', 'typeOfExploitConcatenated',
           'typeOfLabourConcatenated', 'typeOfSexConcatenated',
           'RecruiterRelationship'
           )

remove_columns(remove)
```

# Make All Columns Factor

```{r}
library(dplyr)

# Double Data Type Columns
CTDC[sapply(CTDC, is.double)]<-CTDC[sapply(CTDC, is.double)] %>%
  replace(is.na(.), -1)

#Character Data Type Columns
CTDC[sapply(CTDC, is.character)]<-CTDC[sapply(CTDC, is.character)] %>%
  replace(is.na(.), "-1")
```

Add 0 and 1 as Factor Level for all columns

```{r}
head(CTDC)
```

Replace NAs with 0 if 1 exists anywhere else in category or if is____ has value of 0

Salvage Function
```{r}


quad_mapping_func = function(x){
  # maps -1 to 0, 0 to 0, and 1 to 1
  return(0.5*x**2+0.5*x)
}


null_mapping_func = function(x){
  # maps all values to 0
  return(0)
}





salvage = function(indexes, indicatorindex = 0){
  
  #
  # Salvage takes indicies of sub categories, and replaces -1 (NA Values) 
  # with 0 if a 1 occurs in another subcategory. Additionally, if an indicator
  # index is provided, it will check for any discrepencies and replace 
  # if there are none
  # for example, if isSexualExploit is 0, then all sexual exploit categories 
  # become 0. If isSexualExploit is 0 and a 1 still appears, then there is a
  # Discrepency
  # returns indicies of salvaged rows,and discrepencies
  

  salvage_indexes = c()
  discrepency_indexes = c()
  
for (i in 1:nrow(CTDC2)){
  
  # to_salvage = T if there is a value of 1 and negative 1 in row i 
  # within indexes
  # to_salvage = F if row cannot be salvaged or if salvaging is unnecessary
  
  to_salvage = (any(CTDC2[i,indexes] == 1) & 
            any(CTDC2[i,indexes] == -1))
  
  
  # If to_salvage is true then replace -1 with 0
  # Instead of locating values of -1, we will simply use a function
  # that maps -1 to 0, 0 to 0, and 1 to 1 (see quad_mapping_function)
  
  if (to_salvage == TRUE){
    CTDC2[i,indexes] <<- lapply(CTDC2[i,indexes], mapping_func)
    salvage_indexes = append(salvage_indexes,i)
    }
}
  if (indicatorindex != 0){
  # If indicator index is 0, then make sub variables equal to 0
  if (CTDC2[i,indicatorindex] == 0){
    
    if (any(CTDC2[i,indexes] == 1)){ # If value of 1 still appears
      discrepency_indexes = append(discrepency_indexes,i)
    }
    
    if (any(CTDC2[i,indexes] == -1)){
      salvage_indexes = append(salvage_indexes,i)
    }
    
    
    CTDC2[i,indexes] <<- lapply(CTDC2[i,indexes], null_mapping_func)
  }
    
  }
  
  ret_list = list("salvaged" = salvage_indexes,
                  "discrepencies" = discrepency_indexes)
  return(ret_list)
  
}

```

Apply salvage Function to each category

```{r}
# Duplicate CTDC
CTDC2 = as.tibble(CTDC)


# Create Category column indicies

meansofcontrol_idx = c(10:27)
typeoflabour_idx = c(36:48)
isforcedlabour_idx = c(28)
typeofsex_idx = c(49:52)
issexualexploit_idx = c(29)
recruiterrelation_idx = c(54:58)


# Create Function to apply to all

salvage_table = function(){

sexual_exploit = salvage(typeofsex_idx, issexualexploit_idx)
forced_labour = salvage(typeoflabour_idx, isforcedlabour_idx)
means_of_control = salvage(meansofcontrol_idx)
recruiter_relation = salvage(recruiterrelation_idx)

ret_list = list("sexSalvaged" = sexual_exploit$salvaged,
                "sexDiscrep" = sexual_exploit$discrepencies,
                "labourSalvaged" = forced_labour$salvaged,
                "labourDiscrep" = forced_labour$discrepencies,
                "meanscontrolSalvaged" = means_of_control$salvaged,
                "meanscontrolDiscrep" = means_of_control$discrepencies,
                "recruiterSalvaged" = recruiter_relation$salvaged,
                "recruiterDiscrep" = recruiter_relation$discrepencies
                )
 
return(ret_list)

}

salvage_list = salvage_table()


```


```{r}
library(rlist)
list.save(salvage_list, file="../../Datasets/salvage_list.RData")
write.csv(as.data.frame(CTDC2), "../../Datasets/SalvagedCTDC.csv", row.names=FALSE)
```


```{r}
list.load("../../Datasets/salvage_list.RData")
```
















# Initial Trends

Which Values Missing Together
```{r}
# Replace All Missing with 1, and all present values with 0
CTDC_mask = replace(CTDC, CTDC!=-1, 0)
CTDC_mask = replace(CTDC_mask, CTDC_mask == -1, 1)

CTDC_mask = CTDC_mask %>% mutate_if(is.factor,as.character)%>% mutate_if(is.character,as.numeric)
CTDC_mask 
```

Correlation Plot
```{r}

library("Hmisc") # Gives P-Values for correlation
res2 <- rcorr(as.matrix(CTDC_mask))


corr = res2$r # Correlations
corr_p = res2$P # P-values

library(ggcorrplot)
library(ggplot2)

ggcorrplot(corr, colors = c("blue", "#E7E7E7", "red"),
           tl.cex = 11, tl.srt = 90, show.diag = F, legend.title = "Correlation",
          ggtheme = ggplot2::theme_classic) +
  
  theme(text = element_text(family = "Latex", size = 12),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        panel.background = element_rect(fill = '#242424'))
```

Heat Map

```{r}
library(pheatmap)
pheatmap(CTDC_mask[1:10000,], treeheight_row = 0, treeheight_col = 0)
```
```{r}
l = lm(exploitationDTM~.-CountryOfExploitation-citizenship-citizenshipDTM, data = CTDC)
summary(l)
```

