---
title: "Final Report Code"
output: pdf_document
---

```{r}
library(extrafont) 
library(tidyverse)

# execute once to add fonts:
# font_import() 

loadfonts(device='win')
windowsFonts("Latex" = windowsFont("CMU Serif"))
```




```{r}
library(ggplot2)
library(ggthemes)
library(Cairo)
```




# Import Data
```{r, echo = F, message = F}
library(readr)

CTDC = read_csv("../../Datasets/CTDC.csv")[-c(1)]# Remove Terms of Use Column
```

# Section # Manipulating CTDC Dataset

# Count Number of Complete Cases in Unaltered Data Set
```{r}
sum(complete.cases(CTDC)) # Counts number of Complete Cases
```

# Initialize List of Removed Variables

```{r}
removed = c()
```



# Function to Remove Variables From CTDC

```{r}
remove_columns <- function(remove){
  features = names(CTDC)

  # Update features to only include kept variables
  features = c(setdiff(features, remove))
  
  # Update CTDC to only have kept features
  CTDC <<- CTDC[features]
  
  # Complete Cases
  cases = sum(complete.cases(CTDC))
  print(paste(cases, "complete cases"))
}
```



# Section #.# Logically Removing Variables

```{r}
removed = append(removed, c(
           'yearOfRegistration','Datasource','majorityStatus',
           'meansOfControlConcatenated', 'typeOfExploitConcatenated',
           'typeOfLabourConcatenated', 'typeOfSexConcatenated',
           'majorityStatusAtExploit', 'majorityEntry'
           ))

remove_columns(removed)
```

# Section #.# Quantitatively Removing Variables

## Remove Variables With One Unique Value
```{r}


for (x in 1:ncol(CTDC)) { # Loop over all columns
  column = CTDC[x]
  unq_vals = unique(column)
  
  no_na = na.omit(unq_vals) # Remove NA value from list
  
  n_rem = nrow(no_na) # Count Remaining Unique Values

  # If Number of Values <= 1 then add to remove list
  if (n_rem <= 1){
    removed = append(removed, names(CTDC)[x])
  }
  

}


# Remove from Data Set
remove_columns(removed)
```

# NA Visualizations

```{r}
library(ggplot2)
library(ggthemes)
path = './Graphics'


```

# NA Barplot

```{r}
na_cnts = unname(colSums(is.na(CTDC))) #Array of NA counts

#NA Count Dataframe
na_df = data.frame(Variable = names(CTDC), Count = na_cnts)
```

Plot with no Variable Names
```{r}

# Only include top Number (n) of missings
n = 51

top = sort(na_df$Count, decreasing = TRUE)[n]
top = na_df[na_df$Count >= top,]

ggplot(top, aes(x = reorder(Variable, Count),y = Count)) +
  geom_bar(stat = "identity", width = 1) +
  # Theme and Layout Stuff
  theme_grey(base_size = 8) +
  theme(axis.text.y=element_blank(),axis.ticks.y=element_blank(),
        text = element_text(family = "Latex", size = 15)) +
  xlab("Variable") + ylab("Count of NAs") + coord_flip() +
  # Add Vertical line at 75000
  geom_hline(yintercept = 75000, linetype="solid", 
                color = "salmon", linewidth=2, alpha=0.6)

ggsave(file='./Graphics/NABarplot.png', width=6, height=3)
```

```{r}
# Only include variables with missing count over n
n = 75000

top = na_df[na_df$Count >= n,]

ggplot(top, aes(x = reorder(Variable, Count),y = Count)) +
  geom_bar(stat = "identity", width = 1) +
  # Theme and Layout Stuff
  theme_grey(base_size = 8) +
  theme(axis.text = element_text(size = 9),
    text = element_text(family = "Latex", size = 15)) +
   xlab(element_blank()) + ylab("Count of NAs") + coord_flip(ylim=c(75000,95000))
  # Add Vertical line at 75000

ggsave(file='./Graphics/NABarplot2.png', width=6, height=3)
```

Means of Control Analysis/Removal

```{r}
#Means of Control Only
moc = CTDC[c(4:20)]
not_spec = CTDC$meansOfControlNotSpecified

table(not_spec)
```

```{r}
moc[is.na(moc)] = 0

ggplot(moc, aes(x=rowSums(moc))) + geom_histogram(binwidth = 1) +
  theme_grey(base_size = 16) +
  theme(axis.text = element_text(size = 9),
    text = element_text(family = "Latex", size = 15)) + 
  xlab("Means of Control Row Sum") + ylab("Occurances")
  
ggsave(file='./Graphics/MeansOfControlSumHist.png', width=6, height=3)
```

```{r}
remove = c("meansOfControlDebtBondage"             
,"meansOfControlTakesEarnings"           
,"meansOfControlRestrictsFinancialAccess"
,"meansOfControlThreats"                 
,"meansOfControlPsychologicalAbuse"      
,"meansOfControlPhysicalAbuse"           
,"meansOfControlSexualAbuse"             
,"meansOfControlFalsePromises"           
,"meansOfControlPsychoactiveSubstances"  
,"meansOfControlRestrictsMovement"       
,"meansOfControlRestrictsMedicalCare"    
,"meansOfControlExcessiveWorkingHours"   
,"meansOfControlUsesChildren"            
,"meansOfControlThreatOfLawEnforcement"  
,"meansOfControlWithholdsNecessities"    
,"meansOfControlWithholdsDocuments"      
,"meansOfControlOther"                   
,"meansOfControlNotSpecified")

remove_columns(remove)
```

Naniar Missing Visualizations

```{r, warning = F}
library(naniar)
vis_miss(CTDC, warn_large_data = FALSE) +
  theme(axis.text.y = element_blank(),
    text = element_text(family = "Latex", size = 12),
    axis.text.x = element_text(angle = -90, hjust=1),
    axis.title.y = element_text(angle = -90),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
    ) +
  guides(fill = guide_legend(label.theme = element_text(family = "Latex", angle = -90)))
    

ggsave(file='./Graphics/NaniarVis1.png', width = 6, height = 8)
```


Remove isSlaveryAndPractices and isForcedMArriage

```{r}
remove = c("isSlaveryAndPractices","isForcedMarriage")

remove_columns(remove)
```

Missing Variable Intersections


Upset Plot
```{r, warning = F}
library(ggupset)

# For Each row in data set, create a list of what variables are NA

result <- apply(
  X = is.na(CTDC),
  MARGIN = 1,
  FUN = function(x) paste(colnames(CTDC)[x])
)

CTDC$NaList = result
class(CTDC$NaList) = 'list'
upset_plt_dataframe = CTDC['NaList']


# Initialize PNG Save
png(file="./Graphics/UpsetPlt1.png",
    width     = 6,
    height    = 6,
    units     = "in",
    res       = 300,
    pointsize = 4
)

# Make Plot
ggplot(upset_plt_dataframe, aes(x = NaList)) +
    geom_bar() +
    scale_x_upset(n_sets = 6) + 
    labs(x=element_blank(), y="NA Intersection Count") +
    theme(
      text = element_text(family = "Latex", size = 12))

dev.off()

# Remove List

CTDC = subset(CTDC, select = -c(NaList))
```



```{r}
remove = c("typeOfSexRemoteInteractiveServices","typeOfSexPornography",
           "typeOfSexPrivateSexualServices")

remove_columns(remove)
```

Add DTM Stage To Data Set


Create dataframe with Alpha-2 codes,and DTM stage
```{r}
codes = read_csv("../../Datasets/CountryCodes.csv")
dtm = read_csv("../../Datasets/Countries_Data2.0.csv")[c(2,14)]

###### left join in R using merge() function 
df = merge(x=codes,y=dtm, by.x="Alpha-3 code", by.y = "Code", all.x=TRUE)
Code_DTM = df[c(3,6)]
```



Add column in CTDC with DTM stage for "countryOfExploitation"
```{r}

CTDC = merge(x=CTDC,y=Code_DTM, by.x="CountryOfExploitation", by.y = "Alpha-2 code", all.x=TRUE)

#rename DTM_Stage to exploitationDTM
names(CTDC)[ncol(CTDC)] = "exploitationDTM"
```

Add column in CTDC with DTM stage for "citizenship"
```{r}
CTDC = merge(x=CTDC,y=df, by.x="citizenship", by.y = "Alpha-2 code", all.x=TRUE)

#rename DTM_Stage to citizenshipDTM
names(CTDC)[ncol(CTDC)] = "citizenshipDTM"
```

Remove Unnecessary Joined Data

```{r}
names(CTDC)
```


```{r}
remove = c("DTM_Stage.x","Alpha-3 code",
           "Numeric code","English short name lower case"
           ,"ISO 3166-2")

remove_columns(remove)
```


Save Current Data Set (Complete Entries Only)

```{r}
CTDC.2 = CTDC[complete.cases(CTDC) == T,]
write.csv(CTDC.2,"../../Datasets/CTDC_Complete.csv", row.names = F)
```


Visuals for DTM Stage

```{r}
CTDC.2 = read_csv("../../Datasets/CTDC_Complete.csv")
CTDC.2$citizenshipDTM = as.factor(CTDC.2$citizenshipDTM)
CTDC.2$exploitationDTM = as.factor(CTDC.2$exploitationDTM)
```

```{r}
ggplot(CTDC.2, aes(citizenshipDTM, fill = exploitationDTM)) +
  geom_bar() + theme_grey(base_size = 16) +
  theme(axis.text = element_text(size = 9),
    text = element_text(family = "Latex", size = 15)) + 
   scale_fill_grey() +
  labs(x = "Citizenship DTM Stage", y = "Count", fill = "Exploitation DTM")
  
ggsave(file='./Graphics/DTMStage1.png', width = 8, height = 4)
```



